---
title: "TITLE"
author: "Elizabeth Pankratz"
institute: "Department of Psychology<br>The University of Edinburgh"
output:
  xaringan::moon_reader:
    self_contained: true
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      ratio: '16:9'
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include = FALSE}
library(tidyverse)

# To solve some conflicts between packages
select <- dplyr::select

# knitr settings
knitr::opts_chunk$set(
  fig.width=7, fig.height=5, fig.retina=3,
  out.width = "60%", fig.align = "center",
  cache = FALSE,
  echo = FALSE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
knitr::opts_knit$set(root.dir = here::here())

# dplyr and ggplot settings
options(dplyr.summarise.inform = FALSE)
theme_set(theme_bw())
theme_update(
  text = element_text(family = "Fira Sans", size = 18),
  axis.title.y = element_text(angle=0, vjust=0.5, hjust = 0),
  panel.grid = element_blank(),
  strip.background = element_blank()
  )
```

## Hello world

One slide. $a^2 + b^2 = c^2.$

More text.

Lorem ipsum.

Dolor sit amet.

I was wondering if there is a simple way to do the change of font size, colour and style (bold, italic, etc.) for particular words or phrases in individual xaringan slides within rmarkdown.
I was wondering if there is a simple way to do the change of font size, colour and style (bold, italic, etc.) for particular words or phrases in individual xaringan slides within rmarkdown.
I was wondering if there is a simple way to do the change of font size, colour and style (bold, italic, etc.) for particular words or phrases in individual xaringan slides within rmarkdown.
I was wondering if there is a simple way to do the change of font size, colour and style (bold, italic, etc.) for particular words or phrases in individual xaringan slides within rmarkdown.


---

## Cars

```{r}
cars |>
  ggplot(aes(x = speed, y = dist)) +
  geom_point()
```

